\documentclass{contract}
\usepackage{geometry}
\geometry{margin=2in}
\usepackage{amsmath}

\renewcommand{\min}{\text{min}}

\begin{document}
\begin{center}    
    \textbf{ROOMMATE AGREEMENT BETWEEN PIUS LEE} \\
    \textbf{AND HARESH MURALIDHARAN} \\
\end{center}

\vspace{1em}
\article{Roommate Agreement}
This \textbf{Roommate Agreement} \inlinedef{Agreement} is made as of \textbf{August 24th, 2025} \inlinedef{Effective Date} by and between Pius Lee and Haresh Muralidharan \inlinedef{Roommates}, both Carnegie Mellon University students enrolled for the 2025-2026 Academic Year residing in the Stever Dormitory at Room 308 \inlinedef{Room}.

\section{Definitions}

\subsection The \definition{Bedtime} is defined as the instant when one lies down in bed.

\subsection A \definition{Guest} is defined as ANYBODY other than the \ref{Roommates} who is staying longer than thirty minutes.

\subsection A \definition{Meal Block} is defined as \$13.60 in cash OR the remission of food, already purchased, from any Carnegie Mellon dining service.

\subsection \definition{Personal Space} refers to the individual area assigned to each Roommate. Each Roommate is responsible for respecting each other’s personal space and maintaining the cleanliness and organization of their own area.

\subsection \definition{RA} shall mean Sujit Uppuluri (\texttt{sujitu}), the Resident Assistant having jurisdiction over the \ref{Roomates}' \ref{Room}.

\subsection A \definition{Strike} is an enumeration of violations that is cumulative for the term of this contract.

\subsection A \definition{Tardy} shall mean, if non-negative, the difference between the Bedtime and the maximum allowable Bedtime pursuant to 1.5(a).

\subsection The \definition{Window} is the sliding compartment providing natural light and ventilation in the \ref{Room}.


\section{Scope of Authority} This \ref{Agreement} is binding when filed with the \ref{RA} and other parties, as needed from time to time. If the signatures of the \ref{Roommates} and \ref{RA} are absent, this \ref{Agreement} is rendered null and void. This agreement terminates on May 15th, 2026.

\section{Amendments} Any amendments made to this document must be filed with the \ref{RA} (and any other applicable party). All proposed amendments shall be submitted in writing, clearly outlining the specific sections to be modified and the rationale for such changes. Amendments shall not take effect until they have been formally reviewed, approved, and recorded by the \ref{RA}, and, where required, acknowledged by all relevant parties. The \ref{RA} reserves the right to request additional information, clarification, or supporting documentation prior to approval. A complete record of all amendments, including dates of adoption and responsible parties, shall be maintained as part of the official version of this document.

\section{General Expectations}

\subsection The Roommates agree to maintain open and honest communication by default, fostering a cooperative environment built on mutual respect and flexibility. 

\subsection Unless otherwise specified, the principle of personal property is recognized and upheld, ensuring that individual belongings are not used without prior consent.

\subsection Roommates are expected to notify each other before entering the room. Repeated violation of this Section is grounds for a \ref{Minor Punishment}.

\subsection Roommates are not expected to study in the Room barring exceptional circumstances.

\subsection Spontaneous, received phone calls may occur in the Room. All other phone calls must be outside of the Room.

\subsection Sections 1.4(d-e) apply if and only if the opposing Roommate is also present in the Room.

\section{Bedtime Routine} As per an earlier understanding, the Roommates agreed to use the dormitory for the \textit{primary} purpose of storage and sleep. As such, the following policy is motivated from this understanding.

\subsection The latest Bedtime one must adhere to, subject to change on a daily basis by written communication, is 10:00PM ET. Violation of this Section will produce a Tardy.

\subsection The punishment procedure for the violation of Section 1.5(a) is as follows,

\subsubsection If the Tardy was $5\min < T \leq 15\min$, then the Roommate receives one Strike.

\subsubsection If the Tardy was $15\min < T \leq 90\min$, then the Roommate receives a \ref{Minor Punishment}.

\subsubsection If the Tardy was $90\min < T \leq 300\min$, then the Roommate either receives a Major Punishment or three Minor Punishments, as determined by the opposing Roommate. 


\section{Cleaning}

\subsection Cleaning must occur once weekly, either during Saturdays and Sundays. During Cleaning, private property policy becomes lenient. Schedules A and B rotates every week.

\subsection The Schedule A (generally outside) cleaning routine contains:

\subsubsection changing the trash bag;

\subsubsection taking out the trash;

\subsubsection washing the sheets from the other Roommate once obtained; and

\subsubsection washing the dishes and utensils

\subsection The Schedule B (generally inside) cleaning routine contains:

\subsubsection changing sheets;

\subsubsection cleaning drawers, as needed;

\subsubsection making the bed;

\subsubsection organizing items in the room, as needed;

\subsubsection opening the Window;

\subsubsection pillow sheets, as needed;

\subsubsection washing the floor;

\subsection Disagreements in this policy warrant immediate amendment. While this policy applies to the Roommates, all disagreements are settled by the \ref{RA}.

\section{Guest Policy} Pursuant to compliance with the Carnegie-Mellon Housing Policy, overnight Guest(s) are permitted to stay upon approval from the opposing Roommate. The opposing roommate may assert arbitrary policy on the incoming Guest as a condition of stay.

\section{Gymnasium} The Roommates agree to simultaneously attend the gymnasium together for at least two (2) times a week. Failure to do so subjects the violating Roommate to a Minor Punishment.

\section{Cooking} The Roommates agree to share a large, nontrivial portion of the Red Meal Plan FLEX dollars for breakfast ingredients at Scotty's Market. As such, baring extenuating circumstances, each Roommate may not deny a request to purchase groceries at Scotty's Market. Repeated violation of this Section constitutes a Major Punishment.

\section{Special Rules}

\subsection During Weekdays, the last Roommate to leave the Room MUST open the \ref{Window} to ensure proper ventilation. On weekends, this responsibility rotates according to the cleaning schedule.  

\subsection The Roommates agree that no OPEN food or beverages will be left on desks overnight unless properly stored.

\subsection Laundry must be completed in a timely manner, and common laundry areas should be left clean after use. Overflowing laundry that is left for more than 24 hours is subject to the Minor violation provision.

\section{Violations}

\subsection A Strike, as enumerated in Section 1.1, intends to distribute "fractional" Minor Punishment. Accumulating three (3) Strikes will warrant a \ref{Minor Punishment}.  

\subsection A \definition{Minor Punishment} shall mean the forced relinquishment of one (1) Meal Block.

\subsection A \definition{Major Punishment} shall mean the relinquishment of three (3) Meal Blocks AND the notification of the \ref{RA}.


\newpage
\textbf{Ver. 1.0.0 --- Initial Document}

IN WITNESS WHEREOF, the undersigned parties have executed this \ref{Agreement} as of the date first above written.
\\

\vspace{2em}
\signature{Pius Lee, \texttt{piusl}}

\vspace{2em}
\signature{Haresh Muralidharan, \texttt{hareshmu}}

\vspace{2em}
\signature{Witnessed by Sujit Uppuluri, \texttt{sujitu}}
\vspace{4em}
This is a test commit (2).
\end{document}

